---
title: "IML Term Project"
output: html_notebook
---

```{r}
npf <- read.csv("npf_train.csv")
rownames(npf) <- npf[,"date"] 
npf <- npf[,-1]
npf <- npf[,-3]
# View(npf)
```

```{r}
head(npf)
```

iii. Use the plot() function to produce side-by-side boxplots of event vs. nonevent days.

```{r}
boxplot(RHIRGA84.mean ~ class4,npf)
```

```{r}
npf$class2 <- factor("event",levels=c("nonevent","event"))
npf$class2[npf$class4=="nonevent"] <- "nonevent"
```


Use the summary() function to see how many event days there are. Now use the plot() function to produce side-by-side boxplots of RHIRGA84.mean versus event.

```{r}
summary(npf$class2)
```

```{r}
boxplot(CS.mean ~ class2,npf)
par(mfrow=c(2,2))
hist(npf$CO2168.mean)
hist(npf$CO2168.std)
hist(npf$H2O168.mean)
hist(npf$H2O168.std)

```

omat

```{r}
par(mfrow=c(3,3))
boxplot(Glob.mean ~ class2,npf)
boxplot(UV_A.mean ~ class2,npf)
boxplot(RHIRGA168.mean ~ class2,npf)
boxplot(PAR.mean ~ class2,npf)
boxplot(NET.mean ~ class2,npf)
boxplot(UV_A.mean ~ class2,npf)
boxplot(T84.mean ~ class2,npf)
boxplot(PTG.mean ~ class2,npf)
boxplot(UV_B.mean ~ class2,npf)
```
### ISOIMMAT EROT NONEVENT VS EVENT:
* RHIRGA168 (+muut)
* PAR
* UV_A
* NET

### TEHTÄVÄ 10 pohjalta naive bayes

Jaa test and training

```{r}
## 75% of the sample size
npf_size <- floor(0.75 * nrow(npf))

## set the seed to make your partition reproducible
set.seed(123)
train_ind <- sample(seq_len(nrow(npf)), size = npf_size)

train <- npf[train_ind, ]
away <- c(3:24)
train <- train[,-away]
away2 <- c(4:40)
train <- train[,-away2]
away3 <- c(5:9)
train <- train[,-away3]
away4 <- c(6:32)
train <- train[,-away4]
away5 <- c(7:12)
train <- train[,-away5]

test <- npf[-train_ind, ]
test <- test[,-away]
test <- test[,-away2]
test <- test[,-away3]
test <- test[,-away4]
test <- test[,-away5]

train$class2 <- factor("event",levels=c("nonevent","event"))
train$class2[train$class4=="nonevent"] <- "nonevent"

test$class2 <- factor("event",levels=c("nonevent","event"))
test$class2[test$class4=="nonevent"] <- "nonevent"
```

```{r}
head(test)
```


Compute and report the means and standard deviations of each of the attributes in the training set

```{r}
# different event and nonevent
npf_event <- subset(train, train$class2=="event" )
npf_non <- subset(train, train$class2=="nonevent")
```


```{r}
# means for event class
muE <- c(mean(npf_event$PAR.mean),mean(npf_event$RHIRGA168.mean),mean(npf_event$UV_A.mean),mean(npf_event$NET.mean))
```
```{r}
# sd:t
sdE <- c(sd(npf_event$PAR.mean),sd(npf_event$RHIRGA168.mean),sd(npf_event$UV_A.mean),sd(npf_event$NET.mean))
```

```{r}
# means for nonevent
muN <- c(mean(npf_non$PAR.mean),mean(npf_non$RHIRGA168.mean),mean(npf_non$UV_A.mean),mean(npf_non$NET.mean))
```

```{r}
sdN <- c(sd(npf_non$PAR.mean),sd(npf_non$RHIRGA168.mean),sd(npf_non$UV_A.mean),sd(npf_non$NET.mean))
```


```{r}
# event 1 nonevent 0
f <- function(x,mu,sigma) {
  t <- exp(-(x-mu)^2/(2*sigma^2))/sqrt(2*pi*sigma^2)
  return(t)
} 
phat <- function(x){
  0.5*prod(f(x,muE,sdE))/(0.5*prod(f(x,muE,sdE))+0.5*prod(f(x,muN,sdN)))
} 

acc <- ifelse(apply(test[,3:6],1,phat)>=0.5,"event","nonevent")==test$class2
print(acc)
table(acc)["TRUE"]
table(acc)["FALSE"]
```

#### DUMMY CLASSIFYIER

```{r}
# miten löydetty 396
# boxplot useammasta muuttujasta (ekan viikon malliratkaisuista löytyy korrelaatio matrix -> valittu yksi arvo per korreloivat ja katsottu boxplotit)
# jako event / nonevent dataan
# miten jakaantuu niiden välille
quantile(npf_event$PAR.mean, 0.217)
quantile(npf_non$PAR.mean, 0.77)
# näyttäisi että saadaan melko hyvä jako aikaan jos jaetaan noin 397 kohdalta, jolloin 77% nonevent jää alle 397 ja 78,3% event menee yli 397
```

```{r}
acc_dummy <- ifelse(test$PAR.mean>396,"event","nonevent")==test$class2
table(acc_dummy)["TRUE"]
table(acc_dummy)["FALSE"]
```







